Follow-up Samples

### 2017-04-21 submission/supplemental.Rmd
last minute changes

---
title: ""
bibliography:
csl: microbiome.csl
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
fontsize: 12pt
geometry: margin=1.0in
---

# Differences in the Stool Microbiome Before and After Colorectal Cancer Treatment

>>>>

---
title: ''
csl: microbiome.csl
fontsize: 12pt
output:
  word_document: default
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: null
---

# The effect of treatment on the microbiota of patients diagnosed with colonic lesions
